Create Figures and Tables

### 2023-07-24 Codes/A2_state_fe.rmd
updates

@@

```{r}
data_corn <- readRDS(here("Shared/Data/ProcessedData/data_corn.rds"))

#--- define the semi-parametric portion of the model ---#
semi_formula <-
  formula(yield ~ s(balance, by = sat_cat, k = 3, m = 2))

#--- semi-parametric FE wih fixest ---#
semi_res <-
  semi_ols(
    semi_formula = semi_formula,
    c_formula = "i(sat_cat, ref = 'dryland') + i(year) + i(sc_dry)",
    # fe = "",
    cluster = "sc_dry",
    data = data_corn
  )

#--- main regression results ---#
y_res_int <- semi_res$fe_res

r2_corn_wb <- r2(y_res_int, type = "r2")

gam_y_res <- semi_res$gam_res

#--- raw data for prediction ---#
data_for_pred_corn <-
  CJ(
    balance = seq(min(data_corn$balance), max(data_corn$balance), length = 50),
    sat_cat = unique(data_corn$sat_cat)
  ) %>%
  .[, sat := case_when(
    sat_cat == "[39.4,82]" ~ 40,
    sat_cat == "(82,194]" ~ 194,
    sat_cat == "(194,708]" ~ 348,
    sat_cat == "dryland" ~ 0
  )] %>%
  .[is.na(sat), sat := 0] %>%
  # === can be any sc_code (need to shift yield for "average" county) ===#
  # .[, sc_code := data_corn$sc_code[2]] %>%
  .[, sc_code := data_corn[sat_cat != "dryland"]$sc_code[1]] %>%
  .[, sc_dry := paste0(data_corn$sc_dry[1])] %>%
  # === can be any year (need to shift yield for "average" year) ===#
  .[, year := 2009] %>%
  # === fake yield data (necessary to take advantage of predict.gam) ===#
  .[, yield := 0] %>%
  .[, type := "pred"] %>%
  .[, dry_or_not := fifelse(sat_cat == "dryland", 1, 0) %>% factor()]

#--- create bases  ---#
yhat_data_corn <-
  gen_smooth_data(
    data = data_for_pred_corn,
    gam_res = gam_y_res
  ) %>%
  .$data

y_hat_with_se <- predict(y_res_int, newdata = yhat_data_corn, se.fit = TRUE)

yhat_data_corn[, `:=`(
  y_hat = y_hat_with_se$fit,
  y_hat_se = y_hat_with_se$se.fit
)]

yhat_data_corn[, sat_cat_q :=
  as.numeric(sat_cat) %>%
  ordinal() %>%
  paste0(., " quintile")]

ir_share_data_corn <-
  data_corn %>%
  .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
  .[, balance_avg := mean(balance), by = sc_code] %>%
  .[, type := "Corn"]

@@

```{r}
data_soy <- readRDS(here("Shared/Data/ProcessedData/data_soy.rds"))

#--- define the semi-parametric portion of the model ---#
semi_formula <- formula(yield ~ s(balance, by = sat_cat, k = 3, m = 2))

#--- semi-parametric FE wih fixest ---#
semi_res <-
  semi_ols(
    semi_formula = semi_formula,
    c_formula = "i(sat_cat, ref = 'dryland') + i(year) + i(sc_dry)",
    # fe = "",
    cluster = "sc_dry",
    data = data_soy
  )

#--- main regression results ---#
y_res_int <- semi_res$fe_res

r2_soy_wb <- r2(y_res_int, type = "r2")

gam_y_res <- semi_res$gam_res

#--- raw data for prediction ---#
data_for_pred_soy <-
  CJ(
    balance = seq(min(data_soy$balance), max(data_soy$balance), length = 50),
    sat_cat = unique(data_soy$sat_cat)
  ) %>%
  .[, sat := case_when(
    sat_cat == "[39.4,82]" ~ 40,
    sat_cat == "(82,194]" ~ 194,
    sat_cat == "(194,708]" ~ 348,
    sat_cat == "dryland" ~ 0
  )] %>%
  .[is.na(sat), sat := 0] %>%
  # === can be any sc_code (need to shift yield for "average" county) ===#
  .[, sc_code := data_soy$sc_code[1]] %>%
  .[, sc_dry := data_soy$sc_dry[1]] %>%
  # === can be any year (need to shift yield for "average" year) ===#
  .[, year := 2009] %>%
  # === fake yield data (necessary to take advantage of predict.gam) ===#
  .[, yield := 0] %>%
  .[, type := "pred"] %>%
  .[, dry_or_not := fifelse(sat_cat == "dryland", 1, 0) %>% factor()]

#--- create bases  ---#
yhat_data_soy <-
  gen_smooth_data(
    data = data_for_pred_soy,
    gam_res = gam_y_res
  ) %>%
  .$data

y_hat_with_se <- predict(y_res_int, newdata = yhat_data_soy, se.fit = TRUE)

yhat_data_soy[, `:=`(
  y_hat = y_hat_with_se$fit,
  y_hat_se = y_hat_with_se$se.fit
)]

yhat_data_soy[, sat_cat_q :=
  as.numeric(sat_cat) %>%
  ordinal() %>%
  paste0(., " quintile")]

ir_share_data_soy <-
  data_soy %>%
  .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
  .[, balance_avg := mean(balance), by = sc_code] %>%
  .[, type := "Soybean"]

@@

```{r}
plot_data_ir_share <-
  rbind(
    plot_data_ir_share_with_sfe,
    plot_data_ir_share_no_sfe
  )

g_share_comp <-
  ggplot(plot_data_ir_share[sat <= 500, ]) +
  geom_line(aes(y = ir_share_hat, x = sat * 0.3048)) +
  geom_ribbon(
    aes(
      ymin = ir_share_hat - 1.96 * ir_share_hat_se,
      ymax = ir_share_hat + 1.96 * ir_share_hat_se,
      x = sat * 0.3048
    ),
    alpha = 0.4
  ) +
  ylim(0.25, 1) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 20)) +
  xlab("Saturated Thickness (meter)") +
  ylab("Share of Irrigated Acres") +
  facet_grid(type ~ sfe) +
  theme_fig +
  theme(
    strip.text = element_text(face = "bold"),
    strip.background = element_blank()
  )

@@

s_deam_data <-
  ir_share_data_corn[, .(sat_m = sat_m - mean(sat_m)), by = state_name] %>%
  .[, type := "B. Demeaned by State Average"] %>%
  .[, .(sat_m, type)]

c_deam_data <-
  ir_share_data_corn[, .(sat_m = sat_m - mean(sat_m)), by = sc_code] %>%
  .[, type := "C. Demeaned by County Average"] %>%
  .[, .(sat_m, type)]

non_deam_data <-
  ir_share_data_corn[, .(sat_m = sat_m - mean(sat_m))] %>%
  .[, type := "A. Demeaned by Overall Average"]

plot_data <- rbind(s_deam_data, c_deam_data, non_deam_data)

>>>>

```{r}
reg_results_data <- readRDS(here::here("Shared/Results/reg_results_data.rds"))
```

@@

```{r}
ir_share_data_corn <- reg_results_data[crop == "Corn", share_data][[1]]

@@

```{r}
ir_share_data_soy <- reg_results_data[crop == "Soybean", share_data][[1]]

@@

## With State-year FEs (Main)

```{r}
ir_share_data_corn[, state_year := paste0(state_name, year)]

ir_share_res_corn <-
  gam(
    acres_ratio ~
      s(sat, k = 3, m = 2) +
      s(balance_avg, k = 3, m = 2) +
      ti(sat, balance_avg, k = 3) +
      factor(state_year),
    data = ir_share_data_corn,
    # weight = ~acres,
    family = binomial
  )

share_pred_data_corn <-
  CJ(
    sat = seq(
      min(ir_share_data_corn$sat),
      max(ir_share_data_corn$sat),
      length = 100
    ),
    balance_avg = mean(ir_share_data_corn$balance_avg),
    year = 2016,
    state_year = "Nebraska2009"
  )

```{r}
ir_share_data_soy[, state_year := paste0(state_name, year)]

ir_share_res_soy <-
  gam(
    acres_ratio ~
      s(sat, k = 4, m = 2) +
      s(balance_avg, k = 3, m = 2) +
      ti(sat, balance_avg, k = 3, m = 2) +
      factor(state_year),
    data = ir_share_data_soy,
    # weight = ~acres,
    family = binomial
  )

share_pred_data_soy <-
  CJ(
    sat = seq(
      min(ir_share_data_soy$sat),
      max(ir_share_data_soy$sat),
      length = 100
    ),
    balance_avg = mean(ir_share_data_soy$balance_avg),
    year = 2016,
    state_year = "Nebraska2009"
  )

```{r}
plot_data_ir_share_with_syfe <-
  rbind(
    share_pred_data_corn[, .(ir_share_hat, ir_share_hat_se, sat)][, type := "Corn"],
    share_pred_data_soy[, .(ir_share_hat, ir_share_hat_se, sat)][, type := "Soybean"]
  ) %>%
  .[, sfe := "With State-year FE"]
```

```{r}
plot_data_ir_share <-
  rbind(
    plot_data_ir_share_with_sfe,
    plot_data_ir_share_with_syfe,
    plot_data_ir_share_no_sfe
  )

g_share_comp <-
  ggplot(plot_data_ir_share[sat <= 500, ]) +
  geom_line(aes(y = ir_share_hat, x = sat * 0.3048)) +
  geom_ribbon(
    aes(
      ymin = ir_share_hat - 1.96 * ir_share_hat_se,
      ymax = ir_share_hat + 1.96 * ir_share_hat_se,
      x = sat * 0.3048
    ),
    alpha = 0.4
  ) +
  ylim(0.25, 1) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 20)) +
  xlab("Saturated Thickness (meter)") +
  ylab("Share of Irrigated Acres") +
  facet_grid(type ~ sfe) +
  # theme_fig +
  theme(
    strip.text = element_text(face = "bold"),
    strip.background = element_blank()
  )

@@

sy_demeaan_data <-
  copy(ir_share_data_corn)[, .(sat_m = sat_m - mean(sat_m)), by = .(state_name, year)] %>%
  .[, type := "B. Demeaned by State-Year Average"] %>%
  .[, .(sat_m, type)]

c_y_demeaan_data <-
  copy(ir_share_data_corn)[, sat_m := sat_m - mean(sat_m), by = sc_code] %>%
  .[, .(sat_m = sat_m - mean(sat_m)), by = year] %>%
  .[, type := "C. Demeaned by County and Yearly Average"] %>%
  .[, .(sat_m, type)]

y_demeaan_data <-
  copy(ir_share_data_corn)[, .(sat_m = sat_m - mean(sat_m)), by = year] %>%
  .[, type := "A. Demeaned by Yearly Average"] %>%
  .[, .(sat_m, type)]

plot_data <- rbind(sy_demeaan_data, c_y_demeaan_data, y_demeaan_data)
